---
title: "CodeBook"
author: "Sasha"
date: "8/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3 CodeBook  

Variable descriptions are to be found in "features_info.txt" with a much more precise summary,
than I could give you in this moment.  

Here a description of my code:  

First we read in all relevant data with read.table:
```
names <- read.table("features.txt")
y_train <- read.table("y_train.txt")
y_test <- read.table("y_test.txt")
X_test <- read.table("X_test.txt", col.names = names$V2)
X_train <- read.table("X_train.txt", col.names = names$V2)
```
I included the features.txt, to integrate the corresponding column names directly in the 
reading function.  

Next, I merge the different data frames with cbind/rbind: 
```
test <- cbind(y_test, X_test)
train <- cbind(y_train, X_train)
full_data <- rbind(test, train)
```

For a tidy dataset I just want the relevant data:
```
# grep gets me the right columns with a certain regex
my_data <- full_data[,grep("(mean)|(std)", names(full_data))]
# cbind the activities 
my_data <- cbind(full_data$V1, my_data)
# rename activity column
my_data <- rename(my_data, "Activity" = "full_data$V1")
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
